Fast and Error-Adaptive Count-Distinct Sketch \\for Influence Maximization

### 2021-01-11 paper.tex
progress

\item \acro{} can process very large graphs with millions of vertices and hundreds of millions of edges under a minute, without compromising the quality of results. For large graphs, due to its \ggx{race condition indifferent} nature, performance scales near linearly with the number of threads available. While processing the graph, only we few GBs of memory is used, mostly for storing the graph itself.

@@

% The edge $\{u,v\}$ is verified to be in the sample if ${\rho}(u,v)_r$ is smaller than or equal to the threshold $w_{u,v}$. 
The edge $\{u,v\}$ is exists in the sample $r$ if and only if  ${P}(u,v)_r$ is smaller than the edge threshold $w_{u,v}$. One of the benefits of this approach is, sampling an edge is only single XOR and compare-greater-than operations. Also, the following control flow branch can be removed using conditional move operations. 
An efficient implementation of this approach will be discussed later in this section.
\begin{figure}[!ht] 
    \centering
    \includegraphics[width=1\linewidth]{./images/cdf.pdf}
    \caption{Cumulative probability function of hash-based sampling probabilities on various real-life networks.}
    \label{fig:prob-cdf} 
\end{figure}
Using a strong hash function such as {{\sc Murmur3}} ensures all bits independently change if the input is changed. This property allows us to generate good enough pseudo-random values for fair sampling. To prove the fairness of random values generated with the hash-based approach, we generated a large number of samples for various real-life networks and graphed the bias of random values $P(u,v)_r$ used while sampling.

@@

@@

This approach allows us to keep sketches high quality even after many vertices are added to the seed set, 
but on the other hand, forces us to perform Monte-Carlo simulations which can be very costly.

@@

\begin{algorithm}
\caption{\sc{\acro}($G,K,J$)}
\label{algo:main}
\algorithmicrequire{$G = (V,E)$: the influence graph
\\\hspace*{6.6ex}{$K$: number of seed vertices
\\\hspace*{6.7ex}$\mathcal{J}$: number of MC simulations}\\}
\algorithmicensure{$S$: a seed set that maximizes influence on $G$
}
\begin{algorithmic}[1]
    \State {$S \leftarrow \{\emptyset\}$}
    \For{$ v\in V$} {\bf in parallel}
        \For{$ j\in J$}
            \State $M[j]_v \leftarrow clz(hash(v) \oplus hash(j))$ 
        \EndFor
    \EndFor
    \State $M \leftarrow simulate(G,M,\emptyset)$
    \State $mask \leftarrow zeros(J)$
    \State $\varsigma \leftarrow 0$
    \For{$k=1\ldots K$}
        \State $s \leftarrow \underset{v\in V}{\mathrm{argmax}} ~estimate(merge(mask,M_v))$
        \State $S \leftarrow S \cup \{s\}$
        \State $e \leftarrow estimate(merge(mask,M_s))$
        % \State $R_S \leftarrow run\_cascade(G,S,J)$
        \State {Compute seed set $S$'s Reachability set $R_S(S)$ }
        \State $\sigma_G(S) \leftarrow |R_S|/J$
        \State $\delta = \sigma - \varsigma$
        \If{$ (e - \delta) / \delta < \epsilon_l \lor |e-\delta| / \sigma < \epsilon_g$}
            \State $mask \leftarrow merge(mask,M_s)$
        \Else
            \For{$ v\in V$} {\bf in parallel}
                \For{$ j\in J$}
                    \State $M[j]_v \leftarrow clz(hash(v) \oplus hash(j))$ 
                \EndFor
            \EndFor
            \State $M \leftarrow simulate(G,M,R_S)$
            \State $mask \leftarrow zeros(J) $ 
            \State $\varsigma \leftarrow \sigma $ 
        \EndIf
    \EndFor
    \State \Return $S$
\end{algorithmic}
\end{algorithm}

>>>>

\item \acro{} can process very large graphs with millions of vertices and hundreds of millions of edges under a minute, without compromising the quality of results. For large graphs, due to its race condition indifferent nature, performance scales near linearly with the number of threads available. While processing the graph, only we few GBs of memory is used, mostly for storing the graph itself.

@@

% The edge $\{u,v\}$ is verified to be in the sample if ${\rho}(u,v)_r$ is smaller than or equal to the threshold $w_{u,v}$. 
The edge $\{u,v\}$ is exists in the sample $r$ if and only if  ${P}(u,v)_r$ is smaller than the edge threshold $w_{u,v}$. One of the benefits of this approach is, sampling an edge is only single XOR and compare-greater-than operations. Also, the following control flow branch can be removed using conditional move operations. 
An efficient implementation of this approach will be discussed later in this section.
\begin{figure}[!ht] 
    \centering
    \includegraphics[width=1\linewidth]{./images/CDF.pdf}
    \caption{Cumulative probability function of hash-based sampling probabilities on various real-life networks.}
    \label{fig:prob-cdf} 
\end{figure}
Using a strong hash function such as {{\sc Murmur3}} ensures all bits independently change if the input is changed. This property allows us to generate good enough pseudo-random values for fair sampling. To prove the fairness of random values generated with the hash-based approach, we generated a large number of samples for various real-life networks and graphed the bias of random values $P(u,v)_r$ used while sampling.

@@

Sketches are very fast approximation methods that often provide less than gold standard results. In our case, sketches are very competent at finding the first few vertices, but after sketch registers saturate with high values. Register saturation causes the naive count-distinct sketch method to not distinguish between vertices.

\begin{figure}[!ht]
    \begin{center}
    \includegraphics[width=\linewidth]{images/sketch-saturation.pdf}
    \caption{ Effect of register saturation on Amazon dataset using \acro($J=256$) without rebuilding.
     }\label{fig:sketch-saturation} 
    \end{center}
\end{figure}

In figure \ref{fig:sketch-saturation}, we show the effect of register saturation by comparing two methods; one that uses a new sketch, that build on the residual graph after seed sets' reachability is removed,for all iterations. Other, builds the sketch once at the beginning, then only utilizes sketch merge operations to find the seed set. 
Even though at first few vertices influence is comparable, we see observe near-linear drop-off in estimated influence.

@@

This approach allows us to keep sketches high quality even after many vertices are added to the seed set, 
but on the other hand, forces us to perform Monte-Carlo simulations which can be very costly. We reuse the reachability sets of latent seed set, $R_G(S')$, computed by Monte-Carlo simulations. While rebuilding sketches, $R_G(S')$ is used to check whether if a vertex is blocked in a sample.

@@

\begin{algorithm}
\caption{\sc{\acro}($G,K,J$)}
\label{algo:main}
\algorithmicrequire{$G = (V,E)$: the influence graph
\\\hspace*{6.6ex}{$K$: number of seed vertices
\\\hspace*{6.7ex}$\mathcal{J}$: number of MC simulations}\\}
\algorithmicensure{$S$: a seed set that maximizes influence on $G$
}
\begin{algorithmic}[1]
    \State {$S \leftarrow \{\emptyset\}$}
    \For{$ v\in V$} {\bf in parallel}
        \For{$ j\in J$}
            \State $M[j]_v \leftarrow clz(hash(v) \oplus hash(j))$ 
        \EndFor
    \EndFor
    \State $M \leftarrow simulate(G,M,\emptyset)$
    \State $mask \leftarrow zeros(J)$
    \State $\varsigma \leftarrow 0$
    \For{$k=1\ldots K$}
        \State $s \leftarrow \underset{v\in V}{\mathrm{argmax}} ~estimate(merge(mask,M_v))$
        \State $S \leftarrow S \cup \{s\}$
        \State $e \leftarrow estimate(merge(mask,M_s))$
        % \State $R_S \leftarrow run\_cascade(G,S,J)$
        \State {Compute seed set $S$'s Reachability set $R_{G}(S)$ }
        \State $\sigma_G(S) \leftarrow |R_{G}|/J$
        \State $\delta = \sigma - \varsigma$
        \If{$ (e - \delta) / \delta < \epsilon_l \lor |e-\delta| / \sigma < \epsilon_g$}
            \State $mask \leftarrow merge(mask,M_s)$
        \Else
            \For{$ v\in V$} {\bf in parallel}
                \For{$ j\in J$}
                    \State $M[j]_v \leftarrow clz(hash(v) \oplus hash(j))$ 
                \EndFor
            \EndFor
            \State $M \leftarrow simulate(G,M,R_S)$
            \State $mask \leftarrow zeros(J) $ 
            \State $\varsigma \leftarrow \sigma $ 
        \EndIf
    \EndFor
    \State \Return $S$
\end{algorithmic}
\end{algorithm}
